IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2015-01-07 paper/concrete.tex
add some qed's.
presentational issue from reviewer 1

\begin{definition}[Isomorphism of information-flow control languages]
  A language |(C, .->, erasef l)| is \textit{isomorphic} to a
  language |(C', tarrow', erasefp l)| if there exist total functions |f
  : C -> C'| and |finv : C' -> C| such that |f .. finv = idf C| and |finv
  .. f = idf C'|.  Furthermore, |f| and |finv| are functorial (e.g., if
  $x'\ R'\ y'$ then $f(x')\ R\ f(y')$) over both
  $l$-equivalences and |.->|.

@@

\begin{proof}
  Shown by transporting configurations and reduction derivations from
  $L$ to $L'$, applying TSNI, and then transporting the
  resulting configuration, $l$-equivalence and multi-step derivation back.
\end{proof}

@@

\begin{proof}
  Shown by transporting configurations and reduction derivations
  from $L$ to $L'$, applying TINI and transporting the resulting
  equivalence back using functoriality of |finv| over $l$-equivalences.
\end{proof}

>>>>

\begin{definition}[Isomorphism of information flow control languages]
  A language |(C, .->, erasef l)| is \textit{isomorphic} to a
  language |(C', tarrow', erasefp l)| if there exist total functions |f
  : C -> C'| and |finv : C' -> C| such that |f .. finv = idf C| and |finv
  .. f = idf C'|.  Furthermore, |f| and |finv| are functorial (e.g., if
  $x'\ R'\ y'$ then $f(x')\ R\ f(y')$) over both
  $l$-equivalences and |.->|.

@@

\begin{proof}
  Shown by transporting configurations and reduction derivations from
  $L$ to $L'$, applying TSNI, and then transporting the
  resulting configuration, $l$-equivalence and multi-step derivation back.
  \qed
\end{proof}

@@

\begin{proof}
  Shown by transporting configurations and reduction derivations
  from $L$ to $L'$, applying TINI and transporting the resulting
  equivalence back using functoriality of |finv| over $l$-equivalences.
  \qed
\end{proof}

### 2015-01-07 paper/formal.tex
presentational issue from reviewer 1

TSNI states that if we take two |l|-equivalent configurations, and both
configurations reduce to final configurations (i.e.,
configurations for which there are no
possible further transitions), then the end configurations are also
|l|-equivalent.
%
We highlight that this statement is much weaker than TSNI: it only states that
terminating programs do not leak sensitive data, but makes no statement
about non-terminating programs.

>>>>

TINI states that if we take two |l|-equivalent configurations, and both
configurations reduce to final configurations (i.e.,
configurations for which there are no
possible further transitions), then the end configurations are also
|l|-equivalent.
%
We highlight that this statement is much weaker than TSNI: it only states that
terminating programs do not leak sensitive data, but makes no statement
about non-terminating programs.

### 2015-01-07 paper/intro.tex
presentational issue from reviewer 1

In this paper, we present a framework which brings coarse-grained IFC
ideas into a language-based setting:
%take coarse-grained labeling~\cite{Zeldovich:2006,
%lio} to its logical extreme:
an information flow control system should
be thought of as multiple instances of completely isolated language
runtimes or \emph{tasks}, with information flow control applied to
inter-task communication.  We describe a formal system in which an IFC
system can be designed once and then applied to any programming language
which has control over external effects (e.g., JavaScript or C with
access to hardware privilege separation).  We formalize this system
using an approach by
Matthews-Findler~\cite{Matthews:2007:OSM:1190216.1190220} for combining
operational semantics and prove non-interference guarantees
that are independent of the choice of an specific target language.

@@

In this paper, we describe a simple but general methodology for using
isolation of \emph{execution contexts}, e.g.\ an instance of the
JavaScript engine, in order to add information-flow control to an
existing language.  This is a very practical approach, as there are many
languages which have built-in capabilities for strong isolation by
forking an execution context (i.e. Web Workers).  To validate this
methodology, we describe its application to Haskell (LIO), to JavaScript
(Browbound), to C (HipStar) and to Java (Aeolis).  The essential idea is
to combine the formal models of the source language and a minimal IFC
language, using the embedding technique described in Matthews and
Findler '07.

>>>>

In this paper, we present a framework which brings coarse-grained IFC
ideas into a language-based setting:
%take coarse-grained labeling~\cite{Zeldovich:2006,
%lio} to its logical extreme:
an information flow control system should
be thought of as multiple instances of completely isolated language
runtimes or \emph{tasks}, with information flow control applied to
inter-task communication.  We describe a formal system in which an IFC
system can be designed once and then applied to any programming language
which has control over external effects (e.g., JavaScript or C with
access to hardware privilege separation).  We formalize this system
using an approach by
Matthews and Findler~\cite{Matthews:2007:OSM:1190216.1190220} for combining
operational semantics and prove non-interference guarantees
that are independent of the choice of an specific target language.

@@

In this paper, we describe a simple but general methodology for using
isolation of \emph{execution contexts}, e.g.\ an instance of the
JavaScript engine, in order to add information flow control to an
existing language.  This is a very practical approach, as there are many
languages which have built-in capabilities for strong isolation by
forking an execution context (i.e. Web Workers).  To validate this
methodology, we describe its application to Haskell (LIO), to JavaScript
(Browbound), to C (HipStar) and to Java (Aeolis).  The essential idea is
to combine the formal models of the source language and a minimal IFC
language, using the embedding technique described in Matthews and
Findler '07.

### 2015-01-07 paper/real.tex
presentational issue from reviewer 1

Simply disallowing all the external effects is overly-restricting for
real-world applications (e.g., pages typically load images, perform
XHR requests, etc.).
%
In this light, COWL allows safe network communication by associating an
implicit label with remote hosts (a host's label corresponds to
its origin).
%
In turn, when a task perform a request, the COWL's IFC monitor
ensures that the task label can flow to the remote origin label.
%
While the external effects of COWL can be formally modeled, we do not
model them in our formalism, %more general framework,
since, like for the
Node.js case, they are specific to this system.
%
%Indeed, even the labeled HTTP client in  Node.js and COWL differ, even
%though they're both JavaScript systems, simply because of the
%differing environments.

>>>>

Simply disallowing all the external effects is overly-restricting for
real-world applications (e.g., pages typically load images, perform
network requests, etc.).
%
In this light, COWL allows safe network communication by associating an
implicit label with remote hosts (a host's label corresponds to
its origin).
%
In turn, when a task perform a request, the COWL's IFC monitor
ensures that the task label can flow to the remote origin label.
%
While the external effects of COWL can be formally modeled, we do not
model them in our formalism, %more general framework,
since, like for the
Node.js case, they are specific to this system.
%
%Indeed, even the labeled HTTP client in  Node.js and COWL differ, even
%though they're both JavaScript systems, simply because of the
%differing environments.

### 2015-01-07 paper/retrofit.tex
presentational issue from reviewer 1

In Fig.~\ref{fig:ifc}, we give the syntax and \emph{single-task}
evaluation rules for a minimal information-flow control language.
Ordinarily, information flow control languages are defined by directly
stating a base language plus information flow control operators.  In
contrast, our language is purposely minimal: it does not have sequencing
operations, control flow, or other constructs.  However, it contains
support for the following core information flow control features:

@@

The \textsc{I-sandbox} rule is used to create a new isolated task that
executes separately from the existing tasks (and can be communicated
with via |send| and |recv|).  When the new task is created, there
is the question of what the target language state of the new task should
be.  Our rule is stated generically in terms of a function |klone|.
Conservatively, |klone| may be simply thought of as the identity
function, in which
case the semantics of sandbox are such that the state of the target language is \emph{cloned}
when sandboxing occurs.  However, this is not necessary: it is also valid for |klone|
to remove entries from the state.  In Section~\ref{sec:concrete}, we give a more detailed
discussion of the implications of the choice of |klone|, but all our
security claims will hold regardless of the choice of |klone|.

>>>>

In Fig.~\ref{fig:ifc}, we give the syntax and \emph{single-task}
evaluation rules for a minimal information flow control language.
Ordinarily, information flow control languages are defined by directly
stating a base language plus information flow control operators.  In
contrast, our language is purposely minimal: it does not have sequencing
operations, control flow, or other constructs.  However, it contains
support for the following core information flow control features:

@@

The \textsc{I-sandbox} rule is used to create a new isolated task that
executes separately from the existing tasks (and can be communicated
with via |send| and |recv|).  When the new task is created, there
is the question of what the target language state of the new task should
be.  Our rule is stated generically in terms of a function |klone|.
Conservatively, |klone| may be simply thought of as the identity
function, in which
case the semantics of |sandbox| are such that the state of the target language is \emph{cloned}
when sandboxing occurs.  However, this is not necessary: it is also valid for |klone|
to remove entries from the state.  In Section~\ref{sec:concrete}, we give a more detailed
discussion of the implications of the choice of |klone|, but all our
security claims will hold regardless of the choice of |klone|.
